---
title: "Unit Strengths, Weaknesses, and Basic Stats"
output:  
  bookdown::html_document2:
    toc: yes
    toc_depth: 2
    number_sections: yes
pkgdown:
  as_is: true
vignette: >
  %\VignetteIndexEntry{Unit Strengths, Weaknesses, and Basic Stats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

Buying [Battle Realms Zen Edition from Steam](https://store.steampowered.com/app/1025600/Battle_Realms_Zen_Edition/) is one of the best game buys I have ever made. I still remember the few times I spent with the game in computer shops when I was in high school. I only played a few games, and I struggled to play, much more win, against the AI. I wish I could have played Battle Realms more back then. 

With the release of the game is steam, I never thought I would be able to have another chance to at least beat the AIs in the game. I am not that big of a fan of real time strategy games because I am not very good at micro-management, but Battle Realms has a certain appeal that makes want to be better at it.

Since I am a returning noob to the game, I still am not very familiar to the different strengths and weaknesses of each unit. I know experience will let acquaint me with all the units, but that will take months, if not years, of playing and practice. Lucky for me, I know [R](https://www.r-project.org/) and the Battle Realms data is accessible with the [Battle Realms Data Editor](https://forums.gamingterritory.com/topic/28424-battle-realms-data-editor-by-situvn/). I took my knowledge and R and my love for Battle Realms to create this fun package. 

While there is an official Battle Realms [unit chart](https://battlerealms.github.io/chart/), I think the information in it is incomplete especially for a noob and data lover like. Here is my attempt to provide enthusiasts with a way to review unit strengths and weaknesses. For non-useRs, you can go straight to the [table](#data-showcase).

```{r set-options-attach-packages, include = TRUE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)

library(battleRealms)
library(data.table)
library(cdata)
library(magrittr)
library(DT)

# create standard datatable function to be used in all tables in this post
show_datatable <- function(data) {
  data %>% 
    DT::datatable(
      rownames = FALSE,
      extensions = 'FixedColumns',
      options = list(
        pageLength = 50,
        scrollX = TRUE,
        scrollCollapse = TRUE,
        fixedColumns = list(leftColumns = 3),
        columnDefs = list(
          list(
            className = 'dt-center',
            targets = 0:(ncol(data) - 1)
          )
        )
      ),
      filter = list(position = 'top', clear = FALSE, plain = TRUE)
    )
}

```

# Data Preparation

## Select Variables

```{r select-data-and-columns}

units <- br_units[
  ,
  .(
    UnitID = Type,
    Name,
    Clan,
    UnitClass,
    RiceTrainCost,
    WaterTrainCost,
    YinYangTrainCost,
    MaxHealth,
    HealthRecoveryRate,
    MaxHealthRecovery,
    MaxFatigue,
    FatigueRecovery,
    MeleeWeapon,
    MissileWeapon,
    MissileWeaponLaunchHeight,
    PrefersMelee,
    AMBlunt, 
    AMCutting, 
    AMExplosive,
    AMFire,
    AMMagical,
    AMPiercing,
    MaxUnitsAttacking,
    DeathYinYangAwarded,
    StaminaWhenRunning,
    Bracing,
    ImmuneToCharge,
    InnateAbility,
    BattleGear1,
    BattleGear2,
    BattleGear3
  )
]

weapons <- br_weapons[
  ,
  .(
    Type,
    BaseDamage,
    MinRange,
    MaxRange,
    MaxMountedRange,
    WatchtowerMinRange,
    WatchtowerMaxRange,
    Class,
    DamageClass,
    OpportunityFire,
    AreaOfEffect,
    Poison,
    PoisonTime,
    IsFireWeapon,
    FirePointDamage,
    YinPerHit,
    YangPerHit
  )
]

```

## Transform Data

```{r convert-weapons-to-blocks}

units <- pivot_to_blocks(
  units,
  nameForNewKeyColumn = "WeaponType",
  nameForNewValueColumn = "WeaponID",
  columnsToTakeFrom = c("MeleeWeapon", "MissileWeapon")
)

setDT(units)

```

## Combine Unit and Weapons Data

```{r merge-units-weapon}

unit_stats <- units[
  weapons,
  on = c("WeaponID" = "Type"),
  nomatch = 0,
  allow.cartesian = TRUE
]

```


These data is available in the package as the `br_unit_stats`.

# Data Showcase

```{r show-unit-stats, fig.cap="Battle Realms Zen Edition (v1.56.2) Units and Some of Their Useful Stats."}

# Make Damage Class more meaningful

unit_stats[
  ,
  DamageClass := fcase(
    DamageClass == 0, "Blunt",
    DamageClass == 1, "Cutting",
    DamageClass == 2, "Explosive",
    DamageClass == 3, "Fire",
    DamageClass == 4, "Magical",
    DamageClass == 5, "Piercing"
  )
]

# Transform melee and missile damage in separate columns looks better for display
weapon_damage_ct <- 
  data.frame(
    WeaponType = c("MeleeWeapon", "MissileWeapon"),
    BaseDamage = c("MeleeDamage", "MissileWeapon"),
    DamageClass = c("MeleeType", "MissileType")
  )


unit_stats <- blocks_to_rowrecs(
  unit_stats, 
  keyColumns = c("UnitID", "Name"), 
  controlTable = weapon_damage_ct,
  columnsToCopy = names(unit_stats)[
    !names(unit_stats) %in% 
      c("UnitID", "Name", "WeaponType", "BaseDamage", "DamageClass", "WeaponID")
  ]
)

unit_stats[
  ,
  Clan := fcase(
    Clan == 0, "Dragon",
    Clan == 1, "Hero",
    Clan == 2, "Lotus",
    Clan == 3, "Serpent",
    Clan == 5, "Wolf"
  )
]

unit_stats[
  ,
  Name := gsub(
    paste0(
      "^",
      c("Hero", "Dragon", "Lotus", "Serpent", "Wolf"),
      " ",
      collapse = "|"
    ),
    "",
    Name
  )
]

show_datatable(
  unit_stats
)

```

